---
title: 'Team 5 Final Project: Forecasting O3 Pollution in Beijing, China'
author: "Shailja Somani, Caleb McCurdy, & Ebad Akhter"
date: "November 10, 2023"
output: pdf_document
---

```{r, echo = FALSE}
# Set seed for reproducability 
set.seed(506)

# Import packages
library(readxl)
library(tidyverse)
library(fpp2)
library(quantmod)
library(dplyr)
library(readr)
library(zoo)
library(fpp3)
library(gridExtra)
library(lmtest)
library(tsibble)
library(ggplot2)
library(caret)
library(xts)
library(corrplot)
library(tsibbledata)
library(tseries)
library(forecast)
library(rpart)
library(scales)
library(lubridate)
```

## Data Importing, Preprocessing, & EDA

### Importing the Data
The dataset includes data collected hourly from March 2013 to February 2017 at 12 different air pollution monitoring sites in Beijing. We will only use one site's data in this project and determine which to use by identifying which file has the lowest value of nulls in the O3 data, which is identified below. 

```{r}
# List all CSV files in the current working directory
subfolder_name <- "PRSA_Data_20130301-20170228"
csv_files <- list.files(path = subfolder_name, pattern = "*.csv")

# Initialize variables to keep track of the best file and its statistics
best_file_o3 <- NULL
best_o3_count <- Inf

# Iterate through each CSV file
for (file in csv_files) {
  # Read the CSV file into a data frame
  df <- read.csv(file.path(subfolder_name, file))
  
  # Calculate the number of nulls in the "O3" column
  o3_null_count <- sum(is.na(df$O3))

  # Check if this file has fewer nulls in the "O3" column
  if (o3_null_count < best_o3_count) {
    best_o3_count <- o3_null_count
    best_file_o3 <- file
  }

}

# Print the results
cat("CSV file with the lowest null count in 'O3' column:", best_file_o3, "\n")
cat("Null count in 'O3' column:", best_o3_count, "\n")
```

Thus, from here on out, we will only use the Nongzhanguan site data. 

```{r warning=FALSE}
# import the data
air_df <- read_csv("PRSA_Data_20130301-20170228/PRSA_Data_Nongzhanguan_20130301-20170228.csv", show_col_types = FALSE)

# Summarize the data & look at nulls per column specifically
summary(air_df)
```

### Data Pre-Processing

```{r}
# replace nulls with last value
air <- na.locf(air_df, na.rm = FALSE)
# create one datetime field from all individual date & time fields
air$datetime <- as.POSIXct(paste(air$year, air$month, air$day, air$hour, sep="-"), format="%Y-%m-%d-%H")
head(air)
```

## EDA

```{r EDA}
#correlation matrix of (rounded to 2 decimal places)
air_quality_corr = round(cor(air[c('PM2.5','PM10','SO2','NO2','CO','O3','TEMP','WSPM')]), 2)
corrplot(air_quality_corr, method = 'number', order = 'FPC', type = 'upper', diag = FALSE, title="Correlation between the Air Pollutants", mar=c(0,0,1,0))
#carbon monoxide, lead, ground-level ozone, nitrogen dioxide, particulate matter, and sulfur dioxide.

# Daily Ozone (O3) Readings
ggplot(data=air, aes(x=datetime,y=O3)) + 
  geom_line(size =1) +
  xlab("Datetime") + ylab("Ozone (O3)") +
  ggtitle("Daily Ozone Readings from Nongzhanguan") +
  theme_bw() +
  theme(plot.title = element_text(size=14, face="bold"), axis.title = element_text(size=12), axis.text = element_text(size=10))


O3.ts <- ts(air$O3, start = c(2013,1), end = c(2017, 12), freq = 12)

autoplot(O3.ts) +
  theme_classic() +
  labs(x = "Date", y = "Ozone Readings") 

# Daily Sulfur Dioxide (SO2) Readings
ggplot(data=air, aes(x=datetime,y=SO2)) + 
  geom_line(size =1) +
  xlab("Datetime") + ylab("Sulfur Dioxide (SO2)") +
  ggtitle("Daily Sulfur Dioxide Readings from Nongzhanguan") +
  theme_bw() +
  theme(plot.title = element_text(size=14, face="bold"), axis.title = element_text(size=12), axis.text = element_text(size=10))


SO2.ts <- ts(air$SO2, start = c(2013,1), end = c(2017, 12), freq = 12)

autoplot(SO2.ts) +
  theme_classic() +
  labs(x = "Date", y = "Sulfure Dioxide Readings") 


# Daily Carbon Monoxide (CO) Readings
ggplot(data=air, aes(x=datetime,y=CO)) + 
  geom_line(size =1) +
  xlab("Datetime") + ylab("Carbon Monoxide (CO)") +
  ggtitle("Daily Carbon Monoxide Readings from Nongzhanguan") +
  theme_bw() +
  theme(plot.title = element_text(size=14, face="bold"), axis.title = element_text(size=12), axis.text = element_text(size=10))


CO.ts <- ts(air$CO, start = c(2013,1), end = c(2017, 12), freq = 12)

autoplot(CO.ts) +
  theme_classic() +
  labs(x = "Date", y = "Carbon Monoxide Readings") 

# Daily Nitrogen Dioxide (NO2) Readings
ggplot(data=air, aes(x=datetime,y=NO2)) + 
  geom_line(size =1) +
  xlab("Datetime") + ylab("Nitrogen Dioxide (NO2)") +
  ggtitle("Daily Nitrogen Dioxide Readings from Nongzhanguan") +
  theme_bw() +
  theme(plot.title = element_text(size=14, face="bold"), axis.title = element_text(size=12), axis.text = element_text(size=10))

NO2.ts <- ts(air$NO2, start = c(2013,1), end = c(2017, 12), freq = 12)

autoplot(NO2.ts) +
  theme_classic() +
  labs(x = "Date", y = "Nitrogen Dioxide Readings") 

# Daily Fine Particulate Matter (PM2.5) Readings
ggplot(data=air, aes(x=datetime,y=PM2.5)) + 
  geom_line(size =1) +
  xlab("Datetime") + ylab("Fine Particulate Matter (PM2.5)") +
  ggtitle("Daily Fine Particulate Matter Readings from Nongzhanguan") +
  theme_bw() +
  theme(plot.title = element_text(size=14, face="bold"), axis.title = element_text(size=12), axis.text = element_text(size=10))

PM2.5.ts <- ts(air$PM2.5, start = c(2013,1), end = c(2017, 12), freq = 12)

autoplot(PM2.5.ts) +
  theme_classic() +
  labs(x = "Date", y = "Fine Particulate Matter Readings") 


# Daily Diameter-Less-Than-10-Micrometer Particles Readings
ggplot(data=air, aes(x=datetime,y=PM10)) + 
  geom_line(size =1) +
  xlab("Datetime") + ylab("Diameter-Less-Than-10-Micrometer Particles (PM10)") +
  ggtitle("Daily Diameter-Less-Than-10-Micrometer Particles Readings from Nongzhanguan") +
  theme_bw() +
  theme(plot.title = element_text(size=14, face="bold"), axis.title = element_text(size=12), axis.text = element_text(size=10))


PM10.ts <- ts(air$PM10, start = c(2013,1), end = c(2017, 12), freq = 12)

autoplot(PM10.ts) +
  theme_classic() +
  labs(x = "Date", y = "Diameter-Less-Than-10-Micrometer Particles Readings")
```


### Time Series Plots

```{r}
O3_daily <- air %>%
  group_by(Date = format(datetime, "%Y-%m-%d")) %>%
  summarise(Daily_O3 = mean(O3))

O3_monthly <- air %>%
  group_by(Month = format(datetime, "%Y-%m")) %>%
  summarise(Monthly_O3 = mean(O3))

summary(O3_daily)
summary(O3_monthly)
```



```{r}
# create time series object
O3_m_TS <- ts(O3_monthly$Monthly_O3, start = c(2013, 3), frequency = 12)
O3_d_TS <- ts(O3_daily$Daily_O3, start = c(2013, 60), frequency = 365)

# plot the time series with the mean labeled in red
autoplot(O3_m_TS) +
  labs(title = "Monthly O3 Emissions in Nongzhanguan",
       x = "Date",
       y = "Average O3 Emissions") +
  theme_minimal() +
  geom_hline(yintercept = mean(O3_m_TS), linetype = "dashed", color = "red")

# plot the time series with the mean labeled in red
autoplot(O3_d_TS) +
  labs(title = "Daily O3 Emissions in Nongzhanguan",
       x = "Date",
       y = "Average O3 Emissions") +
  theme_minimal() +
  geom_hline(yintercept = mean(O3_d_TS), linetype = "dashed", color = "red")
```


We can create time plots of the other numerical series (Temperature, Pressure, Dew Point Temperature, Precipitation, and Wind Speed). Additionally, we can create scatter plots of the ground-level ozone emissions series against each of these five series (each point in the scatter plot represents one day). From the charts, we can determine which of the five series will potentially be useful as external predictors in a regression model for forecasting O3 emissions?

```{r}
# Time plots of other numerical series

temp_daily <- air %>%
  group_by(Date = format(datetime, "%Y-%m-%d")) %>%
  summarise(Daily_TEMP = mean(TEMP))

pres_daily <- air %>%
  group_by(Date = format(datetime, "%Y-%m-%d")) %>%
  summarise(Daily_PRES = mean(PRES))

dewp_daily <- air %>%
  group_by(Date = format(datetime, "%Y-%m-%d")) %>%
  summarise(Daily_DEWP = mean(DEWP))

rain_daily <- air %>%
  group_by(Date = format(datetime, "%Y-%m-%d")) %>%
  summarise(Daily_RAIN = mean(RAIN))

wspm_daily <- air %>%
  group_by(Date = format(datetime, "%Y-%m-%d")) %>%
  summarise(Daily_WSPM = mean(WSPM))

daily.temp.ts <- ts(temp_daily$Daily_TEMP, start = c(2013, 60), frequency = 365)
daily.pres.ts <- ts(pres_daily$Daily_PRES, start = c(2013, 60), frequency = 365)
daily.dewp.ts <- ts(dewp_daily$Daily_DEWP, start = c(2013, 60), frequency = 365)
daily.rain.ts <- ts(rain_daily$Daily_RAIN, start = c(2013, 60), frequency = 365)
daily.wspm.ts <- ts(wspm_daily$Daily_WSPM, start = c(2013, 60), frequency = 365)

autoplot(daily.temp.ts) +
  labs(title = "Daily Average Temperature in Beijing",
       y = "") +
  theme_minimal()

autoplot(daily.pres.ts) +
  labs(title = "Daily Average Pressure in Beijing",
       y = "") +
  theme_minimal()

autoplot(daily.dewp.ts) +
  labs(title = "Daily Average Dew Point Temperature in Beijing",
       y = "") +
  theme_minimal()

autoplot(daily.rain.ts) +
  labs(title = "Daily Average Precipitaion in Beijing",
       y = "") +
  theme_minimal()

autoplot(daily.wspm.ts) +
  labs(title = "Daily Average Wind Speed in Beijing",
       y = "") +
  theme_minimal()
```

```{r}
# create new data frame with daily averages of O3 and external predictors
air_daily <- O3_daily
names(air_daily)[names(air_daily) == "Daily_O3"] <- "O3"

air_daily$TEMP <- temp_daily$Daily_TEMP
air_daily$PRES <- pres_daily$Daily_PRES
air_daily$DEWP <- dewp_daily$Daily_DEWP
air_daily$RAIN <- rain_daily$Daily_RAIN
air_daily$WSPM <- wspm_daily$Daily_WSPM
```

```{r}
# scatter plots

ggplot(air_daily, aes(x = TEMP, y = O3)) +
  geom_point() +
  labs(title = "Temperature vs O3 Emissions")

ggplot(air_daily, aes(x = PRES, y = O3)) +
  geom_point() +
  labs(title = "Pressure vs O3 Emissions")

ggplot(air_daily, aes(x = DEWP, y = O3)) +
  geom_point() +
  labs(title = "Dew Point Temperature vs O3 Emissions")

ggplot(air_daily, aes(x = RAIN, y = O3)) +
  geom_point() +
  labs(title = "Precipitation vs O3 Emissions")

ggplot(air_daily, aes(x = WSPM, y = O3)) +
  geom_point() +
  labs(title = "Wind Speed vs O3 Emissions")
```

### Try Differencing & Smoothing

```{r smoothing method 1}
# Apply ETS smoothing
ets_model <- ets(O3_d_TS, model = "AAN")

# Get the fitted values (smoothed values)
smoothed_values <- fitted(ets_model)

# Plot the original and smoothed time series
plot(O3_d_TS, col = "blue", type = "l", lty = 1, xlab = "Time", ylab = "O3 Levels", main = "Original vs. Smoothed Time Series (ETS)")
lines(smoothed_values, col = "red", type = "l", lty = 2)
legend("topright", legend = c("Original", "Smoothed"), col = c("blue", "red"), lty = c(1, 2))
```


```{r smoothing method 2}
# Apply STL decomposition and forecasting
stlf_model <- stlf(O3_d_TS)

# Plot the original and smoothed time series
plot(O3_d_TS, col = "blue", type = "l", lty = 1, xlab = "Time", ylab = "O3 Levels", main = "Original vs. Smoothed Time Series (STL)")
lines(stlf_model$fitted, col = "red", type = "l", lty = 2)
# Add a legend
legend("topright", legend = c("Original", "Smoothed"), col = c("blue", "red"), lty = c(1, 2))
```


```{r differencing}
# Test if differencing is needed for stationarity 
# ADF test before differencing
adf_before <- adf.test(O3_d_TS)
cat("ADF Statistic (Before differencing):", adf_before$statistic, "\n")
cat("p-value (Before differencing):", adf_before$p.value, "\n")
cat("Critical values (Before differencing):", adf_before$critical, "\n")

# Differencing
O3_differenced <- diff(O3_d_TS)

# ADF test after differencing
adf_after <- adf.test(O3_differenced)
cat("\nADF Statistic (After differencing):", adf_after$statistic, "\n")
cat("p-value (After differencing):", adf_after$p.value, "\n")
cat("Critical values (After differencing):", adf_after$critical, "\n")

# Plot after differencing with the mean labeled in red
autoplot(O3_differenced) +
  labs(title = "Differenced Daily O3 Emissions in Nongzhanguan",
       x = "Date",
       y = "Average O3 Emissions") +
  theme_minimal() +
  geom_hline(yintercept = mean(O3_differenced), linetype = "dashed", color = "red")
```

## Modeling

### Modeling Exact Values

```{r}
# Create Time Series Object
O3.daily.ts <- ts(air_daily$O3, start = c(2013,60), frequency = 365)

# Training and test partitions
O3.train2 <- window(O3.daily.ts, end = c(2016, 61))
O3.test2 <- window(O3.daily.ts, start = c(2016, 62))
```

```{r}
naive365 <- rwf(O3.train2, h = 365)
snaive365 <- snaive(O3.train2, h = 365)
modeled365 <- forecast(O3.train2, h = 365)
```

```{r}
autoplot(O3.train2) + 
  autolayer(naive365, color = "green", PI = F) +
  autolayer(O3.test2, color = "red") +
  labs(title = "Time Series Plot of O3 Emissions with Naive Forecast",
       x = "Time",
       y = "Ground Ozone") 

autoplot(O3.train2) + 
  autolayer(snaive365, color = "green", PI = F) +
  autolayer(O3.test2, color = "red") +
  labs(title = "Time Series Plot of O3 Emissions with Seasonal Naive Forecast",
       x = "Time",
       y = "Ground Ozone") 

autoplot(O3.train2) + 
  autolayer(modeled365, color = "green", PI = F) +
  autolayer(O3.test2, color = "red") +
  labs(title = "Time Series Plot of O3 Emissions with Modeled Forecast",
       x = "Time",
       y = "Ground Ozone")

autoplot(O3.train2, series = 'Training') +
  labs(title = "Time Series Plot of O3 Emissions with Seasonal Naive Predictions vs. Actual",
       x = "Time",
       y = "Ground Ozone") +
  autolayer(O3.test2, series = 'Actual') +
  autolayer(snaive365, series = 'Prediction', alpha = .4) +
  theme_classic() +
  coord_cartesian(ylim = c(0, 200))

# Extract point forecasts from the modeled365 forecast object
modeled365_forecasts <- as.numeric(modeled365$mean)
# Create a time series object for the forecasts
modeled365_ts <- ts(modeled365_forecasts, start = c(2016, 62), frequency = 365)
# plot modeled365 actual vs. pred
autoplot(O3.train2, series = 'Training') +
  labs(title = "Time Series Plot of O3 Emissions with Modeled Predictions vs. Actual",
       x = "Time",
       y = "Ground Ozone") +
  autolayer(O3.test2, series = 'Actual') +
  autolayer(modeled365_ts, series = 'Prediction', alpha = .4) +
  theme_classic() +
  coord_cartesian(ylim = c(0, 200))
```

```{r}
accuracy_naive365 <- accuracy(naive365, O3.test2)
accuracy_snaive365 <- accuracy(snaive365, O3.test2)
accuracy_modeled365 <- accuracy(modeled365, O3.test2)

accuracy_naive365
accuracy_snaive365 
accuracy_modeled365 
```

```{r arima, warning=FALSE}
# Trying ARIMA model with variety of parameters
# Create time series object
air_daily_ts <- ts(air_daily, start = c(2013, 60), frequency = 365)

# Training and test partitions for the combined time series
combined_train <- window(air_daily_ts, end = c(2016, 61))
combined_test <- window(air_daily_ts, start = c(2016, 62))

# Time series auto arima forecasting without external predictors
# Target column index
target_col_index <- which(colnames(combined_train) == "O3")

# Define a range of ARIMA parameters to search through
arima_params <- list(order = c(0, 1, 2), seasonal = list(order = c(0, 1, 1), period = 365))

# Fit ARIMA model using auto.arima with specified parameters
arima_model_1 <- auto.arima(combined_train[, target_col_index], 
                          seasonal = TRUE, approximation = FALSE,
                          trace = TRUE, stationary = FALSE, parallel = TRUE)
```

```{r}
arima_model_1

# Forecast with the selected ARIMA model
modeled365_arima <- forecast(arima_model_1, h = 365)
```

```{r}
# Plot for Modeled 365
autoplot(combined_train[, "O3"]) +
  autolayer(modeled365_arima, color = "green", PI = FALSE) +
  autolayer(combined_test[, "O3"], color = "red") +
  labs(title = "Time Series Plot of O3 Emissions with ARIMA Forecast",
       x = "Time",
       y = "Ground Ozone")

# Combined Plot with Seasonal Naive, Actual, and Prediction
autoplot(combined_train[, "O3"], series = 'Training') +
  labs(title = "Time Series Plot of O3 Emissions with ARIMA Forecast vs. Actual Values",
       x = "Time",
       y = "Ground Ozone") +
  autolayer(combined_test[, "O3"], series = 'Actual') +
  autolayer(modeled365_arima, series = 'Prediction', alpha = 0.4) +
  theme_classic() +
  coord_cartesian(ylim = c(0, 200))
```

```{r}
accuracy_modeled365_arima <- accuracy(modeled365_arima, combined_test[, "O3"])
accuracy_modeled365_arima
```


#### Modeling with External Predictors

```{r arima w external predictors, warning=FALSE}
# Fit ARIMA model using auto.arima with different parameter combinations
arima_model_2 <- auto.arima(combined_train[, target_col_index], xreg = combined_train[, -target_col_index], 
                          seasonal = TRUE, approximation = FALSE, trace = TRUE, 
                          stationary = FALSE, parallel = TRUE)
```


```{r arima w external predictors, warning=FALSE}
arima_model_2 

# Forecast with the selected ARIMA model
modeled365_combined <- forecast(arima_model_2, h = 365, xreg = combined_test[, -target_col_index])
```

```{r}
# Plot for Modeled 365
autoplot(combined_train[, "O3"]) +
  autolayer(modeled365_combined, color = "green", PI = FALSE) +
  autolayer(combined_test[, "O3"], color = "red") +
  labs(title = "Time Series Plot of O3 Emissions with Modeled Forecast \nand External Predictors",
       x = "Time",
       y = "Ground Ozone")

# Combined Plot with Seasonal Naive, Actual, and Prediction
autoplot(combined_train[, "O3"], series = 'Training') +
  labs(title = "Time Series Plot of O3 Emissions with Modeled Forecast \nand External Predictors",
       x = "Time",
       y = "Ground Ozone") +
  autolayer(combined_test[, "O3"], series = 'Actual') +
  autolayer(modeled365_combined, series = 'Prediction', alpha = 0.4) +
  theme_classic() +
  coord_cartesian(ylim = c(0, 200))
```
```{r}
accuracy_modeled365_combined <- accuracy(modeled365_combined, combined_test[, "O3"])
accuracy_modeled365_combined
```

```{r accuracy df}
# Combine test set accuracy metrics for all 4 forecasts (with & without external predictors thus far)
accuracy_df <- data.frame(
  Model = c("Naive", "Seasonal Naive", "ETS", "ARIMA", "ARIMA with External Predictors"),
  Test_Set_RMSE = c(accuracy_naive365[, "RMSE"][2], accuracy_snaive365[, "RMSE"][2], accuracy_modeled365[, "RMSE"][2],
          accuracy_modeled365_arima[, "RMSE"][2], accuracy_modeled365_combined[, "RMSE"][2]),
  Test_Set_MAE = c(accuracy_naive365[, "MAE"][2], accuracy_snaive365[, "MAE"][2], accuracy_modeled365[, "MAE"][2],
           accuracy_modeled365_arima[, "MAE"][2], accuracy_modeled365_combined[, "MAE"][2]),
  Test_Set_MAPE = c(accuracy_naive365[, "MAPE"][2], accuracy_snaive365[, "MAPE"][2], accuracy_modeled365[, "MAPE"][2],
           accuracy_modeled365_arima[, "MAPE"][2], accuracy_modeled365_combined[, "MAPE"][2])
)

# Print the accuracy data frame
print(accuracy_df)
```


### Modeling if Above/Below Threshold

```{r}
# Create Time Series Object
# Threshold for above standard is 70 micrograms per cubic meter
O3.daily.ts10 <- ifelse(O3.daily.ts > 70, "Yes", "No")
O3.daily.ts10 <- as.numeric(O3.daily.ts10 == "Yes")

O3.train10 <- ifelse(O3.train2 > 70, "Yes", "No")
O3.test10 <- ifelse(O3.test2 > 70, "Yes", "No")
O3.train10 <- as.numeric(O3.train10 == "Yes")
O3.test10 <- as.numeric(O3.test10 == "Yes")
```

```{r, warning=FALSE}
# Create a confusion matrix
cat("Naive Forecast:\n")
naive10_vals <- ifelse(naive365$mean > 70, 1, 0)

cm_naive365 <- confusionMatrix(as.factor(round(naive10_vals)), 
                            as.factor(round(O3.test10)))
cm_naive365

cat("\n\nSeasonal Naive Forecast:\n")
snaive10_vals <- ifelse(snaive365$mean > 70, 1, 0)

cm_snaive365 <- confusionMatrix(as.factor(round(snaive10_vals)), 
                             as.factor(round(O3.test10)))
cm_snaive365

cat("\n\nETS Forecast:\n")
modeled10_vals <- ifelse(modeled365$mean > 70, 1, 0)

cm_modeled365 <- confusionMatrix(as.factor(round(modeled10_vals)), 
                             as.factor(round(O3.test10)))
cm_modeled365

cat("\n\nARIMA Forecast:\n")
modeled_arima_ext10_vals <- ifelse(modeled365_arima$mean > 70, 1, 0)
cm_modeled365_arima <- confusionMatrix(as.factor(round(modeled_arima_ext10_vals)), 
                             as.factor(round(O3.test10)))
cm_modeled365_arima

cat("\n\nARIMA with External Variables Forecast:\n")
modeled_ext10_vals <- ifelse(modeled365_combined$mean > 70, 1, 0)
cm_modeled_ext365 <- confusionMatrix(as.factor(round(modeled_ext10_vals)), 
                             as.factor(round(O3.test10)))
cm_modeled_ext365
```

#### Logistic Regression with External Predictors
```{r}
# Create binary response variable based on O3 levels
combined_train_df <- as.data.frame(combined_train)
combined_train_df$O3_binary <- ifelse(combined_train_df$O3 > 70, 1, 0)
combined_test_df <- as.data.frame(combined_test)
combined_test_df$O3_binary <- ifelse(combined_test_df$O3 > 70, 1, 0)

# Train logistic regression model
log_reg_o3 <- glm(O3_binary ~ TEMP + PRES + DEWP + RAIN + WSPM, data = combined_train_df, family = "binomial")

# Make predictions on the test dataset for simplicity
combined_test_df$prob <- predict(log_reg_o3, newdata = combined_test_df, type = "response")
combined_test_df$forecast <- ifelse(combined_test_df$prob >= 0.5, 1, 0)

# Create confusion matrix
confusionMatrix(data = factor(combined_test_df$forecast, levels = c(0, 1)),
                                reference = factor(combined_test_df$O3_binary, levels = c(0, 1)))
```

```{r}
# Plot LR model - ignore this chunk; quite messy 
# Make df to combine all needed data
# Combine the relevant columns into a data frame
comparison_data <- data.frame(
  Year = as.numeric(time(combined_test)),
  Actual = combined_test_df$O3_binary,
  LogisticRegression = combined_test_df$prob,
  Forecast = combined_test_df$forecast
)

# Add the Previous Training Data to the data frame
comparison_data <- rbind(
  comparison_data,
  data.frame(
    Year = as.numeric(time(combined_train)),
    Actual = combined_train_df$O3_binary,
    LogisticRegression = NA,
    Forecast = NA
  )
)

# Plot the comparison
ggplot(comparison_data, aes(x = Year)) +
  geom_line(aes(y = Actual, color = "Actual")) +
  geom_line(aes(y = LogisticRegression, color = "Logistic Regression")) +
  geom_line(aes(y = Forecast, color = "Forecast")) +
  labs(title = "Comparison of O3 Binary, Logistic Regression Predictions, and Forecast",
       x = "Year",
       y = "Value") +
  scale_color_manual(values = c("Actual" = "blue", 
                                "Logistic Regression" = "green", 
                                "Forecast" = "red")) +
  theme_minimal()
```
### Full Metrics Dataframe
```{r}
# Calculate accuracy for each model
accuracy_naive365 <- sum((naive365$mean > 70) == round(O3.test10)) / length(O3.test10) * 100
accuracy_snaive365 <- sum((snaive365$mean > 70) == round(O3.test10)) / length(O3.test10) * 100
accuracy_modeled365 <- sum((modeled365$mean > 70) == round(O3.test10)) / length(O3.test10) * 100
accuracy_modeled365_arima <- sum((modeled365_arima$mean > 70) == round(O3.test10)) / length(O3.test10) * 100

# Remove the last row from modeled365_combined$mean and O3.test10 to remove 1 NA
modeled365_combined_cleaned <- head(modeled365_combined$mean, -1)
O3_test_cleaned <- head(O3.test10, -1)
accuracy_modeled365_combined <- sum((modeled365_combined_cleaned > 70) == round(O3_test_cleaned)) / length(O3_test_cleaned) * 100

# Add accuracy for each model to the accuracy dataframe
accuracy_df$Test_Set_Accuracy_Pct_Binary_Classification <- c(
  accuracy_naive365,
  accuracy_snaive365,
  accuracy_modeled365,
  accuracy_modeled365_arima,
  accuracy_modeled365_combined
)
```

```{r}
# Add in LR - will just have binary accuracy
accuracy_df <- rbind(
  accuracy_df,
  data.frame(
    Model = "Logistic Regression with External Predictors",
    Test_Set_RMSE = NA,
    Test_Set_MAE = NA,
    Test_Set_MAPE = NA, 
    Test_Set_Accuracy_Pct_Binary_Classification = sum(combined_test_df$forecast == combined_test_df$O3_binary) / nrow(combined_test_df) * 100
  )
)
```

```{r}
print(accuracy_df)
```

