---
title: 'Team 5 Final Project: Forecasting O3 Pollution in Beijing, China'
author: "Shailja Somani, Caleb McCurdy, & Ebad Akhter"
date: "November 10, 2023"
output: pdf_document
---

```{r, echo = FALSE}
# Import packages
library(readxl)
library(tidyverse)
library(fpp2)
library(quantmod)
library(dplyr)
library(readr)
library(zoo)
library(fpp3)
library(gridExtra)
library(lmtest)
library(tsibble)
library(ggplot2)
library(caret)
set.seed(506)
```

## Data Importing, Preprocessing, & EDA

### Importing the Data
The dataset includes data collected hourly from March 2013 to February 2017 at 12 different air pollution monitoring sites in Beijing. We will only use one site's data in this project and determine which to use by identifying which file has the lowest value of nulls in the O3 data, which is identified below. 

```{r}
# List all CSV files in the current working directory
subfolder_name <- "PRSA_Data_20130301-20170228"
csv_files <- list.files(path = subfolder_name, pattern = "*.csv")

# Initialize variables to keep track of the best file and its statistics
best_file_o3 <- NULL
best_o3_count <- Inf

# Iterate through each CSV file
for (file in csv_files) {
  # Read the CSV file into a data frame
  df <- read.csv(file.path(subfolder_name, file))
  
  # Calculate the number of nulls in the "O3" column
  o3_null_count <- sum(is.na(df$O3))

  # Check if this file has fewer nulls in the "O3" column
  if (o3_null_count < best_o3_count) {
    best_o3_count <- o3_null_count
    best_file_o3 <- file
  }

}

# Print the results
cat("CSV file with the lowest null count in 'O3' column:", best_file_o3, "\n")
cat("Null count in 'O3' column:", best_o3_count, "\n")
```

Thus, from here on out, we will only use the Nongzhanguan site data. 

```{r warning=FALSE}
# import the data
air_df <- read_csv("PRSA_Data_20130301-20170228/PRSA_Data_Nongzhanguan_20130301-20170228.csv", show_col_types = FALSE)

# Summarize the data & look at nulls per column specifically
summary(air_df)
```

### Data Pre-Processing

```{r}
# replace nulls with last value
air <- na.locf(air_df, na.rm = FALSE)
# create one datetime field from all individual date & time fields
air$datetime <- as.POSIXct(paste(air$year, air$month, air$day, air$hour, sep="-"), format="%Y-%m-%d-%H")
head(air)
```

## EDA

```{r EDA}

# Dimensions in Data Set
print("Data set Dimensions")
dim(air)

# Data set Summary
print("Dataset Summary")
summary(air)

#count total missing values in each column
print("There are no NULL Values in the Dataset")
sapply(air, function(x) sum(is.na(x)))


#correlation matrix of (rounded to 2 decimal places)
air_quality_corr = round(cor(air[c('PM2.5','PM10','SO2','NO2','CO','O3','TEMP','WSPM')]), 2)
corrplot(air_quality_corr, method = 'number', order = 'FPC', type = 'upper', diag = FALSE, title="Correlation between the Air Pollutants", mar=c(0,0,1,0))
#carbon monoxide, lead, ground-level ozone, nitrogen dioxide, particulate matter, and sulfur dioxide.

# Daily Ozone (O3) Readings
ggplot(data=air, aes(x=datetime,y=O3)) + 
  geom_line(size =1) +
  xlab("Datetime") + ylab("Ozone (O3)") +
  ggtitle("Daily Ozone Readings from Nongzhanguan") +
  theme_bw() +
  theme(plot.title = element_text(size=14, face="bold"), axis.title = element_text(size=12), axis.text = element_text(size=10))

```
### Time Series Plots

```{r}
O3_daily <- air %>%
  group_by(Date = format(datetime, "%Y-%m-%d")) %>%
  summarise(Daily_O3 = mean(O3))

O3_monthly <- air %>%
  group_by(Month = format(datetime, "%Y-%m")) %>%
  summarise(Monthly_O3 = mean(O3))

summary(O3_daily)
summary(O3_monthly)
```



```{r}
# create time series object
O3_m_TS <- ts(O3_monthly$Monthly_O3, start = c(2013, 3), frequency = 12)
O3_d_TS <- ts(O3_daily$Daily_O3, start = c(2013, 60), frequency = 365)

# plot the time series with the mean labeled in red
autoplot(O3_m_TS) +
  labs(title = "Monthly O3 Emissions in Nongzhanguan",
       x = "Date",
       y = "Average O3 Emissions") +
  theme_minimal() +
  geom_hline(yintercept = mean(O3_m_TS), linetype = "dashed", color = "red")

# plot the time series with the mean labeled in red
autoplot(O3_d_TS) +
  labs(title = "Daily O3 Emissions in Nongzhanguan",
       x = "Date",
       y = "Average O3 Emissions") +
  theme_minimal() +
  geom_hline(yintercept = mean(O3_d_TS), linetype = "dashed", color = "red")
```


We can create time plots of the other numerical series (Temperature, Pressure, Dew Point Temperature, Precipitation, and Wind Speed). Additionally, we can create scatter plots of the ground-level ozone emissions series against each of these five series (each point in the scatter plot represents one day). From the charts, we can determine which of the five series will potentially be useful as external predictors in a regression model for forecasting O3 emissions?

```{r}
# Time plots of other numerical series

temp_daily <- air %>%
  group_by(Date = format(datetime, "%Y-%m-%d")) %>%
  summarise(Daily_TEMP = mean(TEMP))

pres_daily <- air %>%
  group_by(Date = format(datetime, "%Y-%m-%d")) %>%
  summarise(Daily_PRES = mean(PRES))

dewp_daily <- air %>%
  group_by(Date = format(datetime, "%Y-%m-%d")) %>%
  summarise(Daily_DEWP = mean(DEWP))

rain_daily <- air %>%
  group_by(Date = format(datetime, "%Y-%m-%d")) %>%
  summarise(Daily_RAIN = mean(RAIN))

wspm_daily <- air %>%
  group_by(Date = format(datetime, "%Y-%m-%d")) %>%
  summarise(Daily_WSPM = mean(WSPM))

daily.temp.ts <- ts(temp_daily$Daily_TEMP, start = c(2013, 60), frequency = 365)
daily.pres.ts <- ts(pres_daily$Daily_PRES, start = c(2013, 60), frequency = 365)
daily.dewp.ts <- ts(dewp_daily$Daily_DEWP, start = c(2013, 60), frequency = 365)
daily.rain.ts <- ts(rain_daily$Daily_RAIN, start = c(2013, 60), frequency = 365)
daily.wspm.ts <- ts(wspm_daily$Daily_WSPM, start = c(2013, 60), frequency = 365)

autoplot(daily.temp.ts) +
  labs(title = "Daily Average Temperature in Beijing",
       y = "") +
  theme_minimal()

autoplot(daily.pres.ts) +
  labs(title = "Daily Average Pressure in Beijing",
       y = "") +
  theme_minimal()

autoplot(daily.dewp.ts) +
  labs(title = "Daily Average Dew Point Temperature in Beijing",
       y = "") +
  theme_minimal()

autoplot(daily.rain.ts) +
  labs(title = "Daily Average Precipitaion in Beijing",
       y = "") +
  theme_minimal()

autoplot(daily.wspm.ts) +
  labs(title = "Daily Average Wind Speed in Beijing",
       y = "") +
  theme_minimal()
```

```{r}
# create new data frame with daily averages of O3 and external predictors
air_daily <- O3_daily
names(air_daily)[names(air_daily) == "Daily_O3"] <- "O3"

air_daily$TEMP <- temp_daily$Daily_TEMP
air_daily$PRES <- pres_daily$Daily_PRES
air_daily$DEWP <- dewp_daily$Daily_DEWP
air_daily$RAIN <- rain_daily$Daily_RAIN
air_daily$WSPM <- wspm_daily$Daily_WSPM
```

```{r}
# scatter plots

ggplot(air_daily, aes(x = TEMP, y = O3)) +
  geom_point() +
  labs(title = "Temperature vs O3 Emissions")

ggplot(air_daily, aes(x = PRES, y = O3)) +
  geom_point() +
  labs(title = "Pressure vs O3 Emissions")

ggplot(air_daily, aes(x = DEWP, y = O3)) +
  geom_point() +
  labs(title = "Dew Point Temperature vs O3 Emissions")

ggplot(air_daily, aes(x = RAIN, y = O3)) +
  geom_point() +
  labs(title = "Precipitation vs O3 Emissions")

ggplot(air_daily, aes(x = WSPM, y = O3)) +
  geom_point() +
  labs(title = "Wind Speed vs O3 Emissions")
```









