---
title: 'Team 5 Final Project: Forecasting O3 Pollution in Beijing, China'
author: "Shailja Somani"
date: "November 10, 2023"
output: pdf_document
---

```{r, echo = FALSE}
# Import packages
library(fpp3)
library(tidyverse)
```

## Data Importing, Preprocessing, & EDA

### Importing the Data
The dataset includes data collected hourly from March 2013 to February 2017 at 12 different air pollution monitoring sites in Beijing. We will only use one site's data in this project and determine which to use by identifying which file has the lowest value of nulls in the O3 data, which is identified below. 

```{r}
# List all CSV files in the current working directory
subfolder_name <- "PRSA_Data_20130301-20170228"
csv_files <- list.files(path = subfolder_name, pattern = "*.csv")

# Initialize variables to keep track of the best file and its statistics
best_file_o3 <- NULL
best_o3_count <- Inf

# Iterate through each CSV file
for (file in csv_files) {
  # Read the CSV file into a data frame
  df <- read.csv(file.path(subfolder_name, file))
  
  # Calculate the number of nulls in the "O3" column
  o3_null_count <- sum(is.na(df$O3))

  # Check if this file has fewer nulls in the "O3" column
  if (o3_null_count < best_o3_count) {
    best_o3_count <- o3_null_count
    best_file_o3 <- file
  }

}

# Print the results
cat("CSV file with the lowest null count in 'O3' column:", best_file_o3, "\n")
cat("Null count in 'O3' column:", best_o3_count, "\n")
```

Thus, from here on out, we will only use the Nongzhanguan site data. 

```{r warning=FALSE}
# import the data
air_df <- read_csv("PRSA_Data_20130301-20170228/PRSA_Data_Nongzhanguan_20130301-20170228.csv", show_col_types = FALSE)

# Summarize the data & look at nulls per column specifically
summary(air_df)
```

### Data Pre-Processing

```{r}
# replace nulls with last value
air <- na.locf(air_df, na.rm = FALSE)
# create one datetime field from all individual date & time fields
air$datetime <- as.POSIXct(paste(air$year, air$month, air$day, air$hour, sep="-"), format="%Y-%m-%d-%H")
head(air)
```

### Time Series Plots

```{r}
O3_daily <- air %>%
  group_by(Date = format(datetime, "%Y-%m-%d")) %>%
  summarise(Average = mean(O3))

O3_monthly <- air %>%
  group_by(Month = format(datetime, "%Y-%m")) %>%
  summarise(Average = mean(O3))

summary(O3_daily)
summary(O3_monthly)
```

```{r}
# create time series object
O3_m_TS <- ts(O3_monthly$Average, start = c(2013, 3), frequency = 12)
O3_d_TS <- ts(O3_daily$Average, start = c(2103, 60), frequency = 365)

# plot the time series with the mean labeled in red
autoplot(O3_m_TS) +
  labs(title = "Monthly O3 Emissions in Nongzhanguan",
       x = "Date",
       y = "Average O3 Emissions") +
  theme_minimal() +
  geom_hline(yintercept = mean(O3_m_TS), linetype = "dashed", color = "red")

# plot the time series with the mean labeled in red
autoplot(O3_d_TS) +
  labs(title = "Daily O3 Emissions in Nongzhanguan",
       x = "Date",
       y = "Average O3 Emissions") +
  theme_minimal() +
  geom_hline(yintercept = mean(O3_d_TS), linetype = "dashed", color = "red")
```




